Ground state energy of diatomic molecules\\ in the Quantum Drude Oscillator model

### 2022-06-20 paper/main.tex
script to generate latex tables

\usepackage{graphicx}
\graphicspath{{./assets/figures/}}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage[table]{xcolor}
\usepackage{empheq} % to use left braces for list of equations
\usepackage{hyperref}

@@

@@

\begin{table}[b]
\caption{\label{tab:table2} aaa}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
 &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
\hline
Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
& 0.680 & 1.870 & 3.700 \\
Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
& 0.450 & 1.930 & 3.760 \\
Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
& 0.750 & 2.170 & 3.560 \\
Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
& 0.900 & 2.370 & 3.720 \\
Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
& 0.380 & 1.730 & 2.830 \\
Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
& 0.760 & 2.110 & 3.120 \\
Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
&  1.120 & 2.620 & 3.480 \\
Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
& 1.330 & 2.800 & 3.590 \\
Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
& 1.420 & 3.030 & 3.740 \\
In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
& 0.960 & 2.460 & 3.780 \\
Tl& 0.480 & 18.90 & 3.550 & & & & \\
\end{tabular}
\end{ruledtabular}
\footnotetext[1]{Here's the first, from Ref.~\onlinecite{feyn54}.}
\footnotetext[2]{Here's the second.}
\footnotetext[3]{Here's the third.}
\footnotetext[4]{Here's the fourth.}
\footnotetext[5]{And etc.}
\end{table}

>>>>

\usepackage{graphicx}
\graphicspath{{./assets/figures/}}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{diagbox}
\usepackage[table]{xcolor}
\usepackage{empheq} % to use left braces for list of equations
\usepackage{hyperref}

@@

\section{Results}

\begin{table}[h!]
\caption{\label{tab:table1} Ground state energy (in Ha) of the H-H system}
\begin{ruledtabular}
\begin{tabular}{c|ccc}
        \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
        \hline
        1.0 & 5.428021 & 1.000000 & 3.673658 \\
        2.0 & 0.531071 & 0.210137 & 0.872826 \\
        3.0 & 1.532129 & 0.957917 & 0.999836 \\
        4.0 & 1.968642 & 0.999963 & 1.000023 \\
        5.0 & 0.031075 & 1.000000 & 1.014180 \\
        6.0 & 0.978062 & 5.375749 & 0.970292 \\
        7.0 & 21.654276 & 0.558010 & -34.785660 \\
        8.0 & 43.488829 & 85.452632 & -28.868817
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}[h!]
\caption{\label{tab:table2} Ground state energy (in Ha) of the He-He system}
\begin{ruledtabular}
\begin{tabular}{c|ccc}
    \diagbox[height=1.8\line]{$r$ (a.u.)}{$\tau$ (\textcolor{teal}{unit})}& 0.0 & 1.0 & 2.0\\
    \hline
    1.0 & 1.000000 & 1.000000 & 5.739538 \\
    2.0 & 1.266281 & 1.134311 & -0.966946 \\
    3.0 & 0.880808 & 0.147328 & -0.206244 \\
    4.0 & 3.755382 & 0.136923 & 1.000000 \\
    5.0 & 1.000000 & 0.999847 & 0.415453 \\
    6.0 & 6.604936 & 1.000000 & -1.709232 \\
    7.0 & 1.000008 & 1.000000 & 9.223832 \\
    8.0& 198.102785 & 1.000000 & 20.246740
\end{tabular}
\end{ruledtabular}
\end{table}

@@
